Data Prep: IUCN and AquaMaps

### 2016-01-14 data_explore/data_explore_global_maps.Rmd
making rasters from aquamaps csvs

@@

@@

am_levelplot1 <- levelplot(all_am_map, par.settings = myTheme, main = 'Entire Aquamaps Dataset')

all_am_ln_map <- log(all_am_map + 1)
all_am_ln_map <- all_am_ln_map/maxValue(all_am_ln_map)
am_levelplot1 <- levelplot(all_am_ln_map, par.settings = myTheme, main = 'Entire Aquamaps Dataset: log-transformed relative species richness', 
          colorkey = list(at = seq(0, 1, length = 15)))

print(am_levelplot1)
print(am_levelplot2)

@@

all_iucn_rast_file   <- file.path(dir_data, 'rasters/iucn_all_rast.tif')

@@

iucn_levelplot1 <- levelplot(all_iucn_map, par.settings = myTheme, main = 'Entire IUCN Dataset')

all_iucn_ln_map <- log(all_iucn_map + 1)
all_iucn_ln_map <- all_iucn_ln_map/maxValue(all_iucn_ln_map)
iucn_levelplot2 <- levelplot(all_iucn_ln_map, 
          par.settings = myTheme, 
          margin = list(axis = TRUE),
          main = 'Entire IUCN Dataset: log-transformed relative species richness', 
          colorkey = list(at = seq(0, 1, length = 15)))

print(iucn_levelplot1)
print(iucn_levelplot2)
# iucn_ln_pts <- as.data.frame(rasterToPoints(all_iucn_ln_map))
# spp_richness_iucn_plot <- ggplot(iucn_ln_pts, aes(x = x, y = y)) +
#   ggtheme_map + 
#   geom_raster(aes(fill = layer), alpha = .7) +
#   scale_fill_continuous(low = 'white', high = 'blue') +
#   borders('world', color='gray40', fill='gray45', size = .1) +  # create a layer of borders
#   scale_x_continuous(breaks = seq(-180, 180, by = 30), expand = c(0, 2)) +
#   scale_y_continuous(breaks = seq( -90,  90, by = 30), expand = c(0, 2)) +
#   labs(title = 'IUCN Dataset: log-transformed relative species richness', x = NULL, y = NULL, fill = NULL) 
# 
# spp_richness_iucn_plot
# ggsave(file.path(dir_fig, 'all_iucn_ln_map.png'), height = 4, width = 8)

>>>>

library(rasterVis)

@@

dir_am_data <- file.path(dir_N, 'git-annex/globalprep/_raw_data/aquamaps/v2015/csv')

@@

am_levelplot1 <- levelplot(all_am_map, main = 'Entire Aquamaps Dataset') # add in par.settings = myTheme

# all_am_ln_map <- log(all_am_map + 1)
# all_am_ln_map <- all_am_ln_map/maxValue(all_am_ln_map)
# am_levelplot1 <- levelplot(all_am_ln_map, par.settings = myTheme, main = 'Entire Aquamaps Dataset: log-transformed relative species richness', 
#           colorkey = list(at = seq(0, 1, length = 15)))

print(am_levelplot1)
# print(am_levelplot2)

@@

all_iucn_rast_file   <- file.path(dir_data, 'rasters/iucn_all_rast.tif')
dir_data_iucn <- file.path(dir_N, 'git-annex/globalprep/_raw_data/iucn_spp')

@@

iucn_levelplot1 <- levelplot(all_iucn_map, main = 'Entire IUCN Dataset') # add in par.settings = myTheme

# all_iucn_ln_map <- log(all_iucn_map + 1)
# all_iucn_ln_map <- all_iucn_ln_map/maxValue(all_iucn_ln_map)
# iucn_levelplot2 <- levelplot(all_iucn_ln_map, 
#           par.settings = myTheme, 
#           margin = list(axis = TRUE),
#           main = 'Entire IUCN Dataset: log-transformed relative species richness', 
#           colorkey = list(at = seq(0, 1, length = 15)))

print(iucn_levelplot1)
# print(iucn_levelplot2)
# iucn_ln_pts <- as.data.frame(rasterToPoints(all_iucn_ln_map))
# spp_richness_iucn_plot <- ggplot(iucn_ln_pts, aes(x = x, y = y)) +
#   ggtheme_map + 
#   geom_raster(aes(fill = layer), alpha = .7) +
#   scale_fill_continuous(low = 'white', high = 'blue') +
#   borders('world', color='gray40', fill='gray45', size = .1) +  # create a layer of borders
#   scale_x_continuous(breaks = seq(-180, 180, by = 30), expand = c(0, 2)) +
#   scale_y_continuous(breaks = seq( -90,  90, by = 30), expand = c(0, 2)) +
#   labs(title = 'IUCN Dataset: log-transformed relative species richness', x = NULL, y = NULL, fill = NULL) 
# 
# spp_richness_iucn_plot
# ggsave(file.path(dir_fig, 'all_iucn_ln_map.png'), height = 4, width = 8)
